Asthma Cohort Analytic Epidemiology

### 2017-12-13 r_scripts/analysis/asthma_cohort_analytic_epi.Rmd
updated function.

# time stratified function; sets up referent observations
ts_casecross <- function(data, start_date, end_date, id, 
                         admit_date, interval){
 data <- ed_cases 
 sym
 # extract id and admit date
 if(id == T){

 }

}

>>>>

# time stratified function; sets up referent observations
casecross <- function(data, id, admit_date, start_date, end_date, interval){
  # if id value is given
  if(is.character(id)){
    # vector of ids
  id_vec <- data[,id]

    } else { # else if no value provided, create an id variable
      id_vec <- seq(1, nrow(data), by=1)
  }
  # vector of admit dates joined to the id vector
  admit_date <- data[,admit_date]
  id_date <- cbind(id_vec, admit_date)

  # create list of vectors of referent dates and admission date
  referent_date_list <- apply(id_date, 1, function(x){
    date_prior <- as.character(seq(as.Date(x[2]), as.Date(start_date), by = (-interval)))
    date_posterior <- as.character(seq(as.Date(x[2]), as.Date(end_date), by = (interval)))
    date_ref <- sort(unique(c(date_prior, date_posterior)))
    id_rep <- rep(x[1], length(date_ref))
    id_date_vec <- cbind(id_rep, date_ref)
    # outcome
    data_list$outcome <- data_list[data_list$date_vec]
    return(id_date_vec)
  }) # end apply
    # timestrat dataframe
  ts_data <- do.call(rbind, referent_date_list)

  # stuff below still needs to be figured out.

  names(referent_date_list) <- id_vec
  head(referent_date_list)
  test_list <- referent_date_list[1]

  casecross_data <- sapply(test_list, function(x){
    id_vec <- rep(names(x), lengths(x))
    date_vec <- unlist(x)
    cc_data <- cbind(id_vec, date_vec)
    return(cc_data)
  })

  do.call
  rep(names(test_list), lengths(test_list))
}

lengths(test_list)

expand.grid(height = seq(60, 80, 5), weight = seq(100, 300, 50),
            sex = c("Male","Female"))

test <- casecross(data = test_ed, id="personkey", admit_date = "todate", 
                  start_date = "2013-05-01", end_date = "2013-10-1", interval = 7)

  date_prior
  date_posterior
